### 2023-09-03 sections/3-datasets.tex
more tweaks

\subsection{ANN-Benchmarks suite}
\label{subsec:datasets:ann-benchmarks-suite}

@@

@@

\begin{itemize}
\item Ark: 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM, Manjaro Linux with kernel 5.15.78-1-MANJARO \#1 SMP PREEMPT. Rust 1.70, Python 3.10.5
\item Amazon AWS: 64-core Intel Xeon Platinum 8375C CPU 2.90GHz, 512GB RAM, Ubuntu 22.04.3-Ubuntu SMP. Rust 1.71.1, Python 3.10.12
\end{itemize}

>>>>

@@

We compared against FAISS 1.7.4~\cite{johnson2019billion} (IVF and HNSW) and a BLAS-accelerated implementation of na\"ive search as reported in~\cite{johnson2019billion}.

@@

\begin{itemize}
\item Comparisons to FAISS, Bruteforce28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM, Manjaro Linux with kernel 5.15.78-1-MANJARO \#1 SMP PREEMPT. Rust 1.70, Python 3.10.5
\item Amazon AWS: 64-core Intel Xeon Platinum 8375C CPU 2.90GHz, 512GB RAM, Ubuntu 22.04.3-Ubuntu SMP. Rust 1.71.1, Python 3.10.12
\end{itemize}

### 2023-09-03 sections/4-results.tex
more tweaks

For $k= 10$, we report a mean $989\times$ (median $248\times$) speedup over faiss-ivf, a mean $1456\times$ (median $582\times$) speedup over bruteforce-blas, 
and a mean $63\times$ (median $49\times$) speedup over HNSW. For $k=100$, we report a mean $109\times$ (median $71\times$) speedup over faiss-ivf, a mean $382\times$ (median $267\times$) speedup over bruteforce-blas, and a mean $10\times$ (median $9\times$) speedup over HNSW.

The source code for CAKES is available under an MIT
license at https://github.com/URI-ABD/clam.

>>>>

For $k= 10$, we report a mean $989\times$ (median $248\times$) speedup over faiss-ivf, a mean $1456\times$ (median $582\times$) speedup over bruteforce-blas, 
and a mean $63\times$ (median $49\times$) speedup over HNSW. For $k=100$, we report a mean $109\times$ (median $71\times$) speedup over faiss-ivf, a mean $382\times$ (median $267\times$) speedup over bruteforce-blas, and a mean $10\times$ (median $9\times$) speedup over HNSW.
For all datasets benchmarked in this manuscript, the auto-tuning method selected repeated $\rho$-nearest neighbor (Section~\ref{subsubsec:methods:knn-search:repeated-rnn}).

The source code for CAKES is available under an MIT
license at \url{https://github.com/URI-ABD/clam}.

### 2023-09-03 sections/5-discussion.tex
more tweaks

Some of the questions raised by this study suggest that future work is justified; a comparison across more datasets and larger datasets is clearly in order, as is further analysis with distance functions that existing methods such as FAISS do not support, such as Wasserstein distance~\cite{vallender1974calculation} (particularly for arbitrary dimensionality), as Tanimoto distance~\cite{bajusz2015tanimoto}, which is particularly applicable to computing distances based on maximal common subgraphs of molecular structures.
Incorporating these or other distance functions in CAKES only requires providing a Rust implementation of the distance function.

>>>>

Some of the questions raised by this study suggest that future work is justified; a comparison across more datasets and larger datasets is clearly in order, as is further analysis with distance functions that existing methods such as FAISS do not support, such as Wasserstein distance~\cite{vallender1974calculation} (particularly for arbitrary dimensionality), as Tanimoto distance~\cite{bajusz2015tanimoto}, which is particularly applicable to computing distances based on maximal common subgraphs of molecular structures.
Incorporating these or other distance functions in CAKES only requires providing a Rust implementation of the distance function.
For all datasets benchmarked, the auto-tuning method selected repeated $\rho$-nearest neighbor (Section~\ref{subsubsec:methods:knn-search:repeated-rnn}).
However, in limited testing on synthetic datasets obeying simple distributions, this was not always the case.
We seek to evaluate these approaches on many more datasets and distance metrics; it could be that repeated $\rho$-NN is always best (and thus the autotuning is unnecessary), but such a determination is premature.
